---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "images/"
)
```

# nlaR

[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)

The goal of nlaR is to provide an R interface to the National Lakes Assessment data. At this point it only serves the 2007 data.

## Installation

You can install nlaR from Github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jsta/nlaR")
```

## Load package

```{r }
library(nlaR)
```

## Retrieve data from EPA Website

Data is stored in the location returned by `rappdirs::user_data_dir()`

```{r eval=FALSE}
nla_get()
```

## Compile to `rds` object

```{r eval=FALSE}
nla_compile()
```

## Load data from local machine

```{r }
dt <- nla_load()
```

## View NLA tables

```{r }
names(dt)
head(dt$MeanDO_Data)
```

## Map NLA lakes

```{r map lakes}
library(sp)
library(maps)

sp::coordinates(dt$SampledLakeInformation) <- ~ LON_DD + LAT_DD
map("usa")
points(dt$SampledLakeInformation,
       col = factor(dt$SampledLakeInformation$URBAN))
axis(1); axis(2)

```
